Comparative effectiveness of BNT162b2 versus Moderna booster doses in England: preliminary report

### 2022-04-23 write-up/report.Rmd
move report

BNT162b2 booster recipients were matched with MOderna booster recipients on the following characteristics: date of booster dose; primary course vaccine brand; date of second vaccine dose, within 7 days; NHS region (East of England, Midlands, London, North East and Yorkshire, North West, South East, South West); evidence of prior SARS-CoV-2 infection (positive SARS-CoV-2 test, "probable" infection documented in primary care, or COVID-19 hospital admission); clinical risk groups used for prioritisation (clinically extremely vulnerable, clinically at-risk, neither); age, within 3 years; and age groups used by JCVI for prioritisation. 
These matching criteria ensure that treatment groups are also matched within JCVI priority group.

@@

>>>>

BNT162b2 booster recipients were matched with Moderna booster recipients on the following characteristics: date of booster dose; primary course vaccine brand; date of second vaccine dose, within 7 days; NHS region (East of England, Midlands, London, North East and Yorkshire, North West, South East, South West); evidence of prior SARS-CoV-2 infection (positive SARS-CoV-2 test, "probable" infection documented in primary care, or COVID-19 hospital admission); clinical risk groups used for prioritisation (clinically extremely vulnerable, clinically at-risk, neither); age, within 3 years; and age groups used by JCVI for prioritisation. 
These matching criteria ensure that treatment groups are also matched within JCVI priority group.

@@

# Supplement

## JCVI vaccine priority groups

The Joint Committee on Vaccine and Immunisation (JCVI) priority groups were defined as follows:

```{r, table-jcvi, echo=FALSE, message=FALSE, warning=FALSE}

tibble(
  `Priority group` = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10a", "10b"),
  `Description` = c(
    "Residents in a care home for older adults\nStaff working in care homes for older adults",
    "All those 80 years of age and over\nFrontline health and social care workers",
    "All those 75-79 years of age",
    "All those 70-74 years of age\nIndividuals aged 16-69 in a high risk group",
    "All those 65-69 years of age",
    "Adults aged 16-64 years in an at-risk group",
    "All those 60-64 years of age",
    "All those 55-59 years of age",
    "All those 50-54 years of age",
    "All those 40-49 years of age",
    "All those 18-39 years of age"
  )
) %>%
mutate(Description = str_replace_all(Description, "\n", "<br>")) %>% 
gt() %>% 
fmt_markdown(columns = TRUE)

See original priority groups here: https://assets.publishing.service.gov.uk/government/uploads/system/uploads/attachment_data/file/1007737/Greenbook_chapter_14a_30July2021.pdf#page=15
See revised priority groups here: https://www.england.nhs.uk/coronavirus/wp-content/uploads/sites/52/2021/07/C1327-covid-19-vaccination-autumn-winter-phase-3-planning.pdf

Note that we excluded care home residents and health care workers in our analysis, so members of JCVI group 1 are not included and JCVI group 2 includes only those aged 80 and over. The original priority group list has 9 groups, with a 10th group implicitly defined as "everybody else". Here we explicitly define this group, and split into two (10a and 10b) because of the earlier booster eligibility in the 40-49 group from 15 November 2021 onwards. (https://www.gov.uk/government/news/jcvi-issues-advice-on-covid-19-booster-vaccines-for-those-aged-40-to-49-and-second-doses-for-16-to-17-year-olds)
